Supplement to Automatic Matching of Bullet Lands

### 2016-01-06 imaging-supplement.Rnw
feature importance including both random forests

\newpage
\section{Complete evaluation of the Hamby study}\label{supp:extended}
\hh{One way to expand the use of the James Hamby study is to not only match all of the unknown bullet lands against the known bullet lands, but to compare every land against every other land. This effectively doubles the number of comparisons from 10,384 pairwise comparisons of useable bullet lands to 21,115 ($= (118+88)\cdot 205/2$) comparisons by adding another 10,731 bullet land comparisons made up of known-to-known and unknown-to-unkown comparisons. }

@@

Figure~\ref{fig:aligned} gives an overview of all the signatures from bullet lands in the Hamby study aligned by barrel. Three to five bullets were fired from each barrel. The figure gives us both some insight into how well signatures match and how consistent individual characteristics are impregnated on bullets fired from each of the barrels. Signatures for some lands match remarkably well - such as land 5 from barrel 1, whereas all lands from barrel 5 show some variability both in the location and depths of peaks and valleys.

@@

\begin{figure}[hbtp]
<<aligned-second, dependson='aligned', echo=FALSE, warning=FALSE, fig.width=15, fig.height=10, out.width='7.5in'>>=
qplot(x=y, y=l30, data=subset(aligned, barrel > 5), 
      geom="line", group=bullet, colour=bullet) + 
  ylim(c(-7,7)) + xlab("") + ylab("") + xlim(c(0,3000)) +
  facet_grid(facets=barrel~land, labeller="label_both") + theme_bw() +
  theme(plot.margin=unit(c(0,0,-1,-1), unit="line"), legend.position="none") + 
  geom_label(aes(y=2.5*(id-3), label=label, colour=bullet), 
             x = 3000, data=subset(labels, barrel > 5), 
             inherit.aes = FALSE, hjust="right", size=3) +
  scale_colour_manual(values=cols)
@
\caption{\label{fig:aligned-second}Overview of aligned signatures for all bullet lands for  barrels 5 to 10 of the Hamby study. }
\end{figure}
\end{landscape}
\newpage
\section{Table of feature importance}\label{supp:randomforest}

<<setup-rtrees, echo=FALSE, message=FALSE>>=
bstats <- read.csv("data-25-25/bullet-stats.csv", stringsAsFactors = FALSE)

>>>>

\newpage
\section{Complete evaluation of the Hamby study}\label{supp:extended}
\hh{One way to expand the use of the James Hamby study is to not only match all of the unknown bullet lands against the known bullet lands, but to compare every land against every other land. This effectively doubles the number of comparisons from 10,384 pairwise comparisons of usable bullet lands to 21,115 $\left[= (118+88)\cdot 205/2\right]$ comparisons by adding another 10,731 bullet land comparisons made up of known-to-known and unknown-to-unkown comparisons. }

@@

Figures~\ref{fig:aligned} and~\ref{fig:aligned-second} give an overview of all the signatures from bullet lands in the Hamby study aligned by barrel. Three to five bullets were fired from each barrel. The figures give us both some insight into how well signatures match and how consistent individual characteristics are impregnated on bullets fired from each of the barrels. Signatures for some lands match remarkably well -- such as land 5 from barrel 1, whereas all lands from barrel 5 show some variability both in the location and depths of peaks and valleys.

@@

\begin{figure}[hbtp]
<<aligned-second, dependson='aligned', echo=FALSE, warning=FALSE, fig.width=15, fig.height=10, out.width='7.5in'>>=
qplot(x=y, y=l30, data=subset(aligned, barrel > 5), 
      geom="line", group=bullet, colour=bullet) + 
  ylim(c(-7,7)) + xlab("") + ylab("") + xlim(c(0,3000)) +
  facet_grid(facets=barrel~land, labeller="label_both") + theme_bw() +
  theme(plot.margin=unit(c(0,0,-1,-1), unit="line"), legend.position="none") + 
  geom_label(aes(y=2.5*(id-3), label=label, colour=bullet), 
             x = 3000, data=subset(labels, barrel > 5), 
             inherit.aes = FALSE, hjust="right", size=3) +
  scale_colour_manual(values=cols)
@
\caption{\label{fig:aligned-second}Overview of aligned signatures for all bullet lands for  barrels 5 to 10 of the Hamby study. }
\end{figure}
\end{landscape}
\newpage
\section{Table of feature importance}\label{supp:randomforest}
Two random forests were calculated for the Hamby study. For the first random forest only comparisons of bullet lands from known bullets and unknown bullets were used. The second random forest is based on a full comparison of every land with every other land, increasing the number of comparisons from originally 10,384 (10,212 known non-matches and 172 known matches) by another 10,931 comparisons (10,637 known non-matches and 94 known matches). Random forests allow an assessment of variable importance (also called feature importance) as the mean decrease in Gini index when including each variable. 
Table~\ref{tab:importance} shows the results for feature importance for both of these random forests. Importance~1 refers to the smaller subset, Importance~2 is the feature importance derived from the random forest based on all pairwise comparisons. 
<<setup-rtrees, echo=FALSE, message=FALSE>>=
bstats <- read.csv("data-25-25/bullet-stats.csv", stringsAsFactors = FALSE)
